Differentially Private Bayesian Inference

### 2018-04-17 main.tex
uodate
update

In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$. Then we have only one column take value from $\{0,1\}$. THe posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the number of $1$ in the data set and $n_0$ is the number of $0$ in the data set.

>>>>

In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$. We can have only one column take value from $\{0,1\}$. The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the number of $1$ in the data set and $n_0$ is the number of $0$ in the data set.
